Structural Assessment on Stateless Blockchain Improvements with LRU-oriented Cache Replacement Policy

### 2020-06-15 abstract.tex
調整格式以通過 ieee blockchain 的檢測

Cryptocurrency based on blockchain is a peer to peer trading
system. In this decentralized system,
each node maintain a complete ledger which
records entire transaction history of all account.
Years after years, requirement to single node will
get higher and higher. Dealing with the issue, stateless
blockchain is a promising approach. To be more specific,
in this system, each transaction is attached with proof
of validity. With this approach, there is no need for a node
to access the data storage device to search past information
of the ledger. Instead, node only verifies the proof attached
to each transaction. Therefore, it will significantly
reduce the space of data storage for each node.
But it will cause additional network traffic and
verification time.

In this paper, we will discuss the following two points
on the account-based.
First,
It is highly possible to infer the validity of
a transaction from other valid transaction appearing recently.
If we cache account information, we can eliminate some
proof in transactions and then reduce network traffic
and verification time.
Second,
There are so many cache replacement polices.
For LRU polices, we designed two composite data
structures which based on red-black tree and order tree.
And conduct some experiments to compare the costs of
cache hit with the penalty of cache miss.
Simulating today's Ethereum's block property,
when cache size can contain several tens of blocks' information,
the cache searching time is significantly lower than
the time to verify Merkle Patricia proofs.

>>>>

Cryptocurrency based on blockchain is a peer to peer trading
system. In this decentralized system,
each node maintains a complete ledger which
records entire transaction history of all accounts.
Years after years, requirement to single node will
get higher and higher. Dealing with the issue, stateless
blockchain is a promising approach. To be more specific,
in this system, each transaction is attached with proof
of validity. With this approach, there is no need for a node
to access the data storage device to search past information
of the ledger. Instead, node only verifies the proof attached
to each transaction. Therefore, it will significantly
reduce the space of data storage for each node.
But it will cause additional network traffic and
verification time.

In this paper, we will discuss the following two points
on account-based blockchain.
First,
It is highly possible to infer the validity of
a transaction from another valid transaction appearing recently.
If we cache account information, we can eliminate some
proof in transactions and then reduce network traffic
and verification time.
Second,
There are so many cache replacement polices.
For LRU polices, we designed two composite data
structures which based on red-black tree and order tree.
And conduct some experiments to compare the costs of
cache hit with the penalty of cache miss.
Simulating today's Ethereum's block property,
when cache size can contain several tens of blocks' information,
the cache searching time is significantly lower than
the time to verify Merkle Patricia proofs.

### 2020-06-15 ctapc/paper.tex
調整格式以通過 ieee blockchain 的檢測

\documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
% \usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\usepackage{hyperref}
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
\begin{document}

\title{The Design of Shallow State Blockchain}

\author{\IEEEauthorblockN{1\textsuperscript{st} TSAI, TSUEN-JE}
\IEEEauthorblockA{\textit{Department of Computer Science \& Information Engineering} \\
\textit{National Taiwan University}\\
Taipei, Taiwan \\
r05922086@ntu.edu.tw}
}

@@

\begin{abstract}
Cryptocurrency based on blockchain is a peer to peer trading
system. In this decentralized system,
each node maintain a complete ledger which
records entire transaction history of all account.
Years after years, requirement to single node will
get higher and higher. Dealing with the issue, stateless
blockchain is a promising approach. To be more specific,
in this system, each transaction is attached with proof
of validity. With this approach, there is no need for a node
to access the data storage device to search past information
of the ledger. Instead, node only verifies the proof attached
to each transaction. Therefore, it will significantly
reduce the space of data storage for each node.
But it will cause additional network traffic and
verification time.

In this paper, we will discuss the following two points
on the account-based.
First,
It is highly possible to infer the validity of
a transaction from other valid transaction appearing recently.
If we cache account information, we can eliminate some
proof in transactions and then reduce network traffic
and verification time.
Second,
There are so many cache replacement polices.
For LRU polices, we designed two composite data
structures which based on red-black tree and order tree.
And conduct some experiments to compare the costs of
cache hit with the penalty of cache miss.
Simulating today's Ethereum's block property,
when cache size can contain several tens of blocks' information,
the cache searching time is significantly lower than
the time to verify Merkle Patricia proofs.
\end{abstract}

@@

The remaining sections are arranged as follows.
section II illuminates the design of stateless blockchain,
including cache strategies and data structures
used by cache; Section III narratives some related works,
and concluding remarks are found in section IV.

@@

\begin{itemize}
\item CPU: AMD Ryzen 7 2700X (8 cores 16 threads, 3.6 GHz, 32K L1d cache, 64k L1i cache, 512K L2 cache、8M L3 cache)
\item memory: DDR4 64 GB
\item OS: Linux manjaro 4.19.36-1-MANJARO x86\_64
\item compiler: GCC 9.1.0
\end{itemize}

@@

We claim that, in our implementation:
Hash table is unordered\_map in C++ standard library.
For persistent hash table, we use famous C++
persistent data structures library \href{https://sinusoid.es/immer/}{immer}.
Doubly-linked list, persistent red-black tree,
persistent order tree are all implemented by ourselves.

@@

From \href{https://etherscan.io/chart/gaslimit}{etherscan}, we can
know that Ethereum's gas limit is about ten million, and
it will cost 21000 gas fee per transaction.
After simple division, a block can contain about 500 transactions.
Therefore, the number of get/put instructions
for one block of our workload is set to 500.

@@

We chose Merkle Patricia tree verification cost to compare
with the order tree implementation,
We choose \href{https://docs.rs/trie-db/0.20.1/trie_db/index.html}{trie-db} module,
which is the part of one of the two major
Ethereum implementations,
\href{https://www.parity.io/ethereum/}{Parity Ethereum}, to conduct experiment.

@@

By the information of \href{https://www.etherchain.org/charts/totalAccounts}{etherchain.org},
the number of Ethereum accounts today has exceeded 80 million,
So we first randomly insert 80 million pieces
of data into the Merkle Patricia
tree (that is, the number of leaves is 80 million),
And based on the assumption of 500 transactions in
one block, we batch verify 500 proofs at a time,
The measured time is 5.536 milliseconds, which is
obviously more time-consuming than direct access to cache.

>>>>

\documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
% \usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}

\columnsep 0.24in
\addtolength{\topmargin}{0.075in}
\addtolength{\textheight}{-0.1in}

\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
\begin{document}

\title{Structural Assessment on Stateless Blockchain Improvements with
LRU-oriented Cache Replacement Policy}

% \author{\IEEEauthorblockN{1\textsuperscript{st} TSAI, TSUEN-JE}
% \IEEEauthorblockA{\textit{Department of Computer Science \& Information Engineering} \\
% \textit{National Taiwan University}\\
% Taipei, Taiwan \\
% r05922086@ntu.edu.tw}
% }

@@

\begin{abstract}
Cryptocurrency based on blockchain is a peer to peer trading
system. In this decentralized system,
each node maintains a complete ledger which
records entire transaction history of all accounts.
Years after years, requirement to single node will
get higher and higher. Dealing with the issue, stateless
blockchain is a promising approach. To be more specific,
in this system, each transaction is attached with proof
of validity. With this approach, there is no need for a node
to access the data storage device to search past information
of the ledger. Instead, node only verifies the proof attached
to each transaction. Therefore, it will significantly
reduce the space of data storage for each node.
But it will cause additional network traffic and
verification time.

In this paper, we will discuss the following two points
on account-based blockchain.
First,
It is highly possible to infer the validity of
a transaction from another valid transaction appearing recently.
If we cache account information, we can eliminate some
proof in transactions and then reduce network traffic
and verification time.
Second,
There are so many cache replacement polices.
For LRU polices, we designed two composite data
structures which based on red-black tree and order tree.
And conduct some experiments to compare the costs of
cache hit with the penalty of cache miss.
Simulating today's Ethereum's block property,
when cache size can contain several tens of blocks' information,
the cache searching time is significantly lower than
the time to verify Merkle Patricia proofs.
\end{abstract}

@@

The remaining sections are arranged as follows.
section II illuminates the design of stateless blockchain,
including cache strategies and data structures
used by cache; Section III show the design and
results of experiments; Section IV narratives some related works,
and concluding remarks are found in section V.

@@

\begin{itemize}
\item CPU: AMD Ryzen 7 2700X (8 cores 16 threads, 3.6 GHz, 32K L1d cache, 64k L1i cache, 512K L2 cache, 8M L3 cache)
\item memory: DDR4 64 GB
\item OS: Linux manjaro 4.19.36-1-MANJARO x86\_64
\item compiler: GCC 9.1.0
\end{itemize}

@@

We claim that, in our implementation:
Hash table is unordered\_map in C++ standard library.
For persistent hash table, we use famous C++
persistent data structures library immer.
Doubly-linked list, persistent red-black tree,
persistent order tree are all implemented by ourselves.

@@

From etherscan, we can
know that Ethereum's gas limit is about ten million, and
it will cost 21000 gas fee per transaction.
After simple division, a block can contain about 500 transactions.
Therefore, the number of get/put instructions
for one block of our workload is set to 500.

@@

We chose Merkle Patricia tree verification cost to compare
with the order tree implementation,
We choose trie-db module,
which is a part of one of the two major
Ethereum implementations,
Parity Ethereum, to conduct experiment.

@@

By the information of etherchain.org,
the number of Ethereum accounts today has exceeded 80 million,
So we first randomly insert 80 million pieces
of data into the Merkle Patricia
tree (that is, the number of leaves is 80 million),
And based on the assumption of 500 transactions in
one block, we batch verify 500 proofs at a time,
The measured time is 5.536 milliseconds, which is
obviously more time-consuming than direct access to cache.
